motor_milestone_attempt

### 2022-01-10 paper/manuscript/motor_milestones_attempt.Rmd
update gitignore, figures

We attempted to whether the SAYcam participants' age of reaching particular developmental milestones (sitting, cruising, and walking) significantly influenced the proportion of hands or faces that they saw, using a mixed-effects regression with per-child random intercepts.
We tried including random slopes by age and milestone, but the models did not converge and/or were singular. Thus, for each milestone the R syntax was: \textit{prop_faces ~ age * milestone + (1 | child_id)}. Children's age of achieving each milestone was dummy-coded (i.e., 0=milestone not reached; 1=milestone reached).

>>>>

We examined the SAYcam participants' age of reaching particular developmental milestones (sitting, cruising, and walking) significantly influenced the proportion of hands or faces that they saw, using a mixed-effects regression with per-child random intercepts.
We tried including random slopes by age and milestone, but the models did not converge and/or were singular. Thus, for each milestone the R syntax was: \textit{prop_faces ~ age * milestone + (1 | child_id)}. Children's age of achieving each milestone was dummy-coded (i.e., 0=milestone not reached; 1=milestone reached).
